Stat_490_Paper

### 2020-05-11 Paper.Rmd
Add files via upload

>>>>

- We explored the CMS feature and sought ways to improve it.  The span value does play an impact on the number of consecutive matching striation marks.  Span values and sampling also play a role  when it comes to machine learning model performance but do not seem to increase the overall value of consecutive matching striae.  This leads us to believe the current way CMS is calculated may need to be adjusted.  When exploring two aligned signatures there was strong evidence for higher CMS values than what was actually calculated.  This was found by individually looking at aligned signature plot and observing the matching peaks and values. Currently the CMS values outputed seems to be too low for some bullet comparisons.
